Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-07 paper.tex
(Pending approval) Change author affiliation.
(Pending approval) Modify remark about proof generalization.

\author{
  S\'ebastien Dalibard\and
  Antonio El Khoury\and
  Florent Lamiraux\and
  Alireza Nakhaei\and
  Michel Ta\"ix\and
  Jean-Paul Laumond
  \footnote{The authors are with CNRS, LAAS, 7 avenue du colonel
    Roche, F-31400 Toulouse Cedex 4, France and Univ de Toulouse,
    LAAS, F-31400 Toulouse Cedex 4, France. S\'ebastien Dalibard is
    now with Nanyang Technological University, Singapore.}
  \footnote{
    This paper summarizes and extends previous work that appeared in the 9th and 11th
    IEEE-RAS International Conference on Humanoid Robots, 2009 and 2011.
  }
}

@@

\subsubsection{Remarks}
\paragraph{Generalization to a complete model:} More work is needed to generalize 
the previous proof to any legged robot model. First, because we use a model with
a point mass, we did not have to consider the angular momentum of the robot
around the CoM, while it accounts for dynamic balance. Moreover, when considering
an actual kinematic and dynamic model,
the positions of feet and CoM are not controlled DoFs, but inputs 
for inverse kinematic tasks. Continuity and regularity results about the robot
controller -- i.e. how much the configuration changes when the input of an inverse
kinematics task changes--, would be needed to generalize the proof. We have not
proven such properties for the inverse kinematics controller we use. 
The  proof presented above still gives the intuition for the
algorithm presented in the following.

>>>>

\author{
  S\'ebastien Dalibard\and
  Antonio El Khoury\and
  Florent Lamiraux\and
  Alireza Nakhaei\and
  Michel Ta\"ix\and
  Jean-Paul Laumond
  \footnote{The authors are with CNRS, LAAS, 7 avenue du colonel
    Roche, F-31400 Toulouse Cedex 4, France and Univ de Toulouse,
    LAAS, F-31400 Toulouse Cedex 4, France. S\'ebastien Dalibard is
    now with Aldebaran Robotics, France.}
  \footnote{
    This paper summarizes and extends previous work that appeared in the 9th and 11th
    IEEE-RAS International Conference on Humanoid Robots, 2009 and 2011.
  }
}

@@

\subsubsection{Remarks}
\paragraph{Generalization to a complete model:} 
\textbf{We did not extend the previous proof to any legged robot model
  since empirically, the table cart model is a very good fit for our
  humanoid robot. Although of little practical interest, the
  generalization of the proof does not seem very difficult to
  achieve. As an insight, the difference between the table cart model
  and the full size humanoid robot is due to the derivative of the
  angular momentum and to the vertical acceleration of the center of
  mass. These perturbations can be made as small as desired along the
  sliding path by following the sliding path as slowly as
  necessary. The derivatives of the angular momentum produced by the
  stepping motion can also be made as small as desired by making the
  step height as small as necessary and by using recent results on
  properties of joint trajectories induced by end-effector motions
  \cite{Zanchettin6084763}.}
